
\begin{abstract}
Successful software systems continue to evolve during their lifetimes. During their evolution, these systems undergo various kinds maintenance tasks
 including corrective maintenance tasks  such as fixing defects, adaptive maintenance tasks such as modifications to adapt to a new/changed environment, perfective maintenance tasks such as performance improvements, and preventive maintenance tasks such as refactorings. However, Software Maintenance faces two major problems. 
 
First, maintenance of evolving software is time consuming and labor-intensive. Software maintenance can consume as much as 90\% of the total software development costs. Hence a majority of efforts on reducing software costs needs to be spent in reducing software maintenance costs.
Second, maintenance of evolving software can result in unintended side effects (regression faults) in the software system. Regression testing  is the process of detecting these faults. As the regression testing is a frequently performed activity during software maintenance phase, it occupies a large portion of the software maintenance budget. The current approaches in regression testing are not effective and efficient in finding regression faults.

In this thesis, we provide various solutions for the two preceding problems.
First, we present Refaclib to reduce the cost of some adaptive changes made to evolving software by automating them. 
Second, we present DiffGen for effective regression testing of evolving Software.
Third, we present eXpress for efficient regression testing.
Fourth, we present ASSIST for integration-testing during maintenance.
Fifth, we present PRIEST for generating regression test suite  for testing software in presence of privacy laws.
\end{abstract}


%% ---------------------------- Copyright page ------------------------------ %%
%% Comment the next line if you don't want the copyright page included.
\makecopyrightpage

%% -------------------------------- Title page ------------------------------ %%
\maketitlepage

%% -------------------------------- Dedication ------------------------------ %%
\begin{dedication}
 \centering To my parents.
\end{dedication}

%% -------------------------------- Biography ------------------------------- %%
\begin{biography}
The author was born in a small town \ldots
\end{biography}

%% ----------------------------- Acknowledgements --------------------------- %%
\begin{acknowledgements}
I would like to thank my advisor for his help.
\end{acknowledgements}


\thesistableofcontents

\thesislistoftables

\thesislistoffigures
